\chapter{Conclusion}\label{ch:conclusion}

Since the beginning of the first practice contest (the one about particles with high-energy), our team was really enthusiastic with regard to this competition. In that practice contest and in the following instance (the one suspended by the controversy) we got outstanding scores. In the final competition about NLP (the third one) we also started topping the official ranking, as we began working since the first days after the competition was open. By the second week, we were leading with a performance far above from the full-grade baseline. Hence, we decided that our exploration was enough. We had carried out the application of the tools we have learned from homework's and classes along the course. First, we strictly followed the methodology of avoiding abuse of the hold-out set, to separate into train, test, validation, cross-validation, etc. Second, we defined a 2-order feature map, representing the bi-grams in a NLP learning problem. Third, we converted the categorical variables into numeric, to be able to feed a wider scope of algorithms. Fourth, we explored a large number of diverse classifiers and obtained the expected results: some ensemble methods stand out from the rest (i.e. Boosting and Bagging). Fifth, we tuned the best performing classifiers' hyper-parameters by successive executions. Finally, we untied classifiers with similar performances by the parsimony principle in order to make our submission more robust. We were optimistic about our final model's outcome, but in the last days, and even hours before the closing, some groups significantly improved their performance, eventually moving our team away from the top.

Looking back in time and, after discussing with the highest-ranked teams when the contest had finished, we learned that there was a little more to be done to get the extra points in the ranking. We realized now that coding by ourselves an ensemble of trained classifiers would have given us the extra classification power we needed to win the competition. We will try this approach in the next opportunity. 